### 2023-03-05 manuscript.tex
Updating front matter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad17a823a0016184735b9a130ff14a3e88c36e98.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ad17a823a0016184735b9a130ff14a3e88c36e98/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333509078

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/a177cf5c28b557f4befa7f1ad912f64e65101efb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/a177cf5c28b557f4befa7f1ad912f64e65101efb}{SORTEE-Github-Hackathon/manuscript@a177cf5}
on 2023-03-05.

@@

@@

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ad17a823a0016184735b9a130ff14a3e88c36e98/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ad17a823a0016184735b9a130ff14a3e88c36e98}{SORTEE-Github-Hackathon/manuscript@ad17a82}
on March 5, 2023.

@@

  \textsuperscript{\protect\hyperlink{correspondence}{✉}}

@@

  · \includegraphics{images/mastodon.svg}
  \href{https://ecoevo.social/@pedrobraga}{@pedrobraga@ecoevo.social}

@@

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
✉ --- Correspondence possible via \href{https://github.com/SORTEE-Github-Hackathon/manuscript/issues}{GitHub Issues}
or email to
Pedro Henrique Pereira Braga \textless ph.pereirabraga@gmail.com\textgreater.
